Understanding the Lomb-Scargle Periodogram

### 2017-01-06 PracticalLombScargle.tex
Add initial Bayesian discussion

On the astronomy side, several examples of such analyses exist.
For example, the Supersmoother approach to detecting periodicity
involves fitting a flexible non-parametric smoothing
function to the data at each frequency: the flexibility of the model leads
to fewer issues of aliasing \citep{Reimann94}.
Another approach is to use empirically-derived templates as a functional fit
at each frequency; this has been employed effectively in \citet{Sesar2010,
Sesar2013} and related work.
Finally, there has been some exploration of extensions to the Lomb-Scargle
periodogram for use with multi-band observations, using various forms of
regularization to control model complexity \citep{VanderPlas2015, Long2016}.

\subsection{A Note About ``Bayesian'' Periodograms}

@@

\subsection{Normalization of the Periodogram}

>>>>

On the astronomy side, several examples of such analyses exist.
For example, the Supersmoother approach to detecting periodicity
involves fitting a flexible non-parametric smoothing
function to the data at each frequency: the flexibility of the model leads
to fewer issues of aliasing \citep{Reimann94}.
Another approach is to use empirically-derived templates as a functional fit
at each frequency; this has been employed effectively in \citet{Sesar2010,
Sesar2013} and related work.
Finally, there has been some exploration of extensions to the Lomb-Scargle
periodogram for use with multi-band observations, using various forms of
regularization to control model complexity \citep{VanderPlas2015, Long2016}.
With many of these types of extensions, computational complexity quickly
becomes an issue, because fast $\mathcal{O}(N\log N)$ approaches along the
lines of \citet{Press89} are not available for more general functional forms
(see \sect{algorithmic-considerations}).

\subsection{A Note About ``Bayesian'' Periodograms}
\sectlabel{bayesian-periodograms}
The least squares view of the Lomb-Scargle periodogram creates a natural
bridge, via maximum likelihood, to Bayesian approaches to periodograms.
In fact, \citet{Jaynes87} showed that the standard form of the Lomb-Scargle
periodogram can be derived directly from the principles of Bayesian Probability
Theory outlined in his comprehensive treatment of the subject \citep{Jaynes03}.
In the Bayesian view, the Lomb-Scargle periodogram is the optimal statistic
for detecting a stationary sinusoidal signal in the presence of Gaussian
noise.

$P(f)$ from \eq{lomb-scargle-periodogram}

\begin{equation}
  p(f~|~D) \propto e^{-n \chi^2 / 2} \propto e^{P(f)}
\end{equation}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig24_bayesian_periodogram}
  \caption{Comparison of the Lomb-Scargle periodogram (upper right) and the
    Bayesian posterior periodogram (lower right) for simulated data (left)
    drawn from a simple sinusoid.
    The Bayesian posterior is equal to the exponentiation of the unnormalized
    Lomb-Scargle periodogram, and thus tends to suppress all but the largest
    peak.
    \figlabel{bayesian-periodogram}}
\end{figure}

Warnings:

\citep{Mortier15}

What works:

Bayesian models with strong priors \citep{Bretthorst88}
Flexible Bayesian models \citep{Gregory92, Kelly14}
Gaussian process models \citep{Angus16}

@@

\subsection{Periodogram Normalization and Interpretation}
\sectlabel{normalizations}
